Advantages of mixed unitary operators for quantum information processing

### 2018-12-10 decorrelation/mixed_unitaries.tex
Updating single qubit numerics photo, and including in figures section

>>>>

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{SQRTX.png}
  \caption{Numerical results comparing a 0MUP to a 1MUP for a single tunable qubit. Shown with lower alpha values are example members of the control families, with diamond norms of around $10^{-2}$. The 0MUP can be seen to outperform the members of the control family by two orders of magnitude at the origin, and the 1MUP by an order of magnitude. However, the 1MUP can be seen to be flatter. In paritcular, for small detunings, the 1MUP performs better than the 0MUP.}
  \label{fig:1QMUP}
\end{figure*}
